Peridynamic Plates and Flat Shells: A non-ordinary, state-based model

### 2014-04-30 PlatePaper.tex
minor edits to results section
More small edits

%\documentclass[11pt]{amsart}
%\documentclass[5p,twocolumn]{elsarticle}
\documentclass[preprint,review,12pt]{elsarticle}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{color}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{epstopdf}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{import}
\usepackage[section]{placeins}
\usepackage[color=red!40, textsize=scriptsize]{todonotes}

@@

\section{Introduction}
\todo{Lets not start this paper with the exact same paragraph as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.  When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.  Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.  Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.  A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.  This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading.  The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
A nonlocal plate model by Ansari et al. \cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.

@@

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.  While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity}\todo{Cite several more papers here, including your forthcoming beam paper}.

@@

Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.  If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  Models in which they are not in the same direction are called \textit{non-ordinary}.  Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.  Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
%\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
    \caption{Illustration of a bond pair model that resists angular deformation}
    \label{fig:SimpleBondpair}
\end{figure}
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} by taking the Fr\'echet derivative. For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}. 
The moment that resists the change in angle between partner bonds is proportional to the sine of the angle between them, therefore the force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
    \caption{Illustration of a bond pair on a plate}
    \label{fig:BondPairPlate}
\end{figure}
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{bondPairV.eps_tex}
    \caption{Deformation and force vector states}
    \label{fig:Bondpair}
\end{figure}
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small. 
Because the potential energy and force states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}. 
Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.
\subsection{Energy Equivalence}
To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Kirckhoff plate in the \emph{local limit}, i.e. when the nonlocal length scale vanishes.  
We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and plate thickness that does not change with deformation. 
While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations. 
For small vertical displacements we have
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{z(\mathbf{x}+\boldsymbol{\xi})-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi})}{|\boldsymbol{\xi}|},
    \label{eq:beamdtheta}
where $z$ is the vertical displacement of material point.  
Taking \(\boldsymbol{\xi}=\xi (\cos(\phi),\sin(\phi))\) in cartesian coordinates and momentarily assuming continuous displacements for the sake of comparison, we use a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta}) about \(\xi = 0\) 
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{\xi}{2} \left(\cos^2(\phi) \kappa_1+\sin^2(\phi) \kappa_2+2\sin(\phi)\cos(\phi)\kappa_3\right)+\mathcal{O}(\xi^3)
    \label{eq:beamdtheta2}
    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
%\label{eq:continuousBeamw}
    w =& \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
    =& \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
    & +4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
If we use a weighting function \(\omega(\boldsymbol{\xi})=\omega(\xi)\) and assume that the $\omega$ plays the role of a localization kernel, i.e. $\omega = 0 \; \forall \; \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic plate is
    W =& \alpha \int_{0}^\delta\int_0^{2 \pi} w\; \xi {\rm d}\phi {\rm d}\xi ,\notag \\
    =& \alpha \frac{3\pi}{8} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)\int_{0}^\delta \omega(\xi)\xi^3{\rm d}\xi + \mathcal{O}(\delta^6).\notag 
Equating $W$ with the classical Kirchoff plate strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
    \lim_{\delta \to 0}  W &= \Omega, \notag \\
    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right), \notag \\
%    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
    \nu = \frac{1}{3},\:\: \alpha &= \frac{16}{3 m} \frac{G h^3}{12(1-\sfrac{1}{3})},
\label{eq:alpha}
%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
    m = \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag.

It must be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.

\subsection{Combining Bending and Extension Models}
The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds, such as in-plane stretch or shear.
If these behaviors are expected in combination with bending, a useful model must resist both.
To create a plate model that also resists these deformations, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
In this model, individual bonds act as springs resisting changes in length.
%
\begin{equation}
    \label{eq:bondextension}
    \vstate{T}{}{\boldsymbol{\xi}} =\beta\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|}
\end{equation}
%
By matching the energy of a plate in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the plate.
Following the example of \cite{silling2007peridynamic}, we begin with a plate under pure in-plane shear.
In Einstein notation, the strain energy of this plate is
%
%\begin{align*}
%    W^d_\text{C} &= G \; h \; \epsilon_{ij} \epsilon_{ij} = G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
%    W^d_\text{PD} &= \frac{\beta}{2}(\underline{\omega}\; \underline{\epsilon^d})\bullet \underline{\epsilon^d}\\
%    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{\underline{\omega}\langle\xi\rangle}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_\xi\\
%\end{align*}
%
\begin{align*}
    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; dA_{\boldsymbol{\xi}} \\
    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;dA_{\boldsymbol{\xi}}\\
    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_{\boldsymbol{\xi}}\\
\end{align*}
%
With $i, j, k, l = 1,2$. For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
%
\begin{align*}
%    m&=(\underline{\omega}\:\underline{x}) \bullet \underline{x}\\
    m &= \int_A \omega(\xi)|\boldsymbol{\xi}|^2\; dA_{\boldsymbol{\xi}} \\
    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11}]\\
    &= \frac{\beta \; m}{16} \epsilon_{ij}^d \epsilon_{kl}^d (\delta_{ij}\delta_{kl}+\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})\\
    &= \frac{\beta \; m}{8} \epsilon_{ij}^d \epsilon_{ij}^d \implies\\
     \beta &= \frac{8 \; G\;h}{m}
\end{align*}
%

Having calibrated the bond-extension model to the shear modulus, applying a different uniform strain (such as might result from uniaxial tension) reveals the bond-based model to result in a one-parameter linearly-elastic model with Poisson's ratio \(\nu=\sfrac{1}{3}\).

Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a plate.
Consider a single bond-pair in the combined model:
\begin{figure}
  \label{fig:hybridmodel}
  \centering
  \input{\diagrampath/bondPairCombinedV.tex}
  \caption{The Hybrid Model Combines Bending and Extension Components}
\end{figure}
As the two sides are pulled apart, the magnitude of the extension force in each bond increases, and the magnitude of the bending force decreases. 
At the same time, the angle at which the extension force acts decreases, and the angle of action for the bending force increases.
For small amounts of bending and reasonable stretches, increased tension in the direction of the bond pair results in increase restorative force.

>>>>

%\documentclass[11pt]{amsart}
%\documentclass[5p,twocolumn]{elsarticle}
\documentclass[preprint,review,12pt]{elsarticle}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{color}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{epstopdf}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{import}
\usepackage[section]{placeins}
\usepackage[color=red!40, textsize=scriptsize, textwidth=1.0in]{todonotes}

@@

\section{Introduction}
\todo{Lets not start this paper with the exact same sentence as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.  When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.  Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.  Other peridynamic models capture tension and compression in 1D bars \cite{silling2003deformation} and 2D membranes \cite{silling2005peridynamic}, but these features do not resist transverse displacement.  A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.  This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading.  The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
A nonlocal plate model by Ansari et al. \cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.

@@

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.  While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity, foster2011energy, jogrady2014a}\todo{Cite several more papers here.}.

@@

Just as stress and strain are work conjugate, so too are the force and deformation vector-states for hyperelastic materials.  If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  Models in which they are not in the same direction are called \textit{non-ordinary}.  Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.  Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
%
%\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.  These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
    \caption{Illustration of a bond pair model that resists angular deformation.}
    \label{fig:SimpleBondpair}
\end{figure}
%
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \todo{Need to define $\boldsymbol{\xi}$ somewhere} \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative. For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
%
\begin{align}
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
%
&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
\end{align}
%
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}.  The moment that resists the change in angle between partner bonds is proportional to the sine of the angle between them, therefore the force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
    \caption{Illustration of a bond pair on a plate.}
    \label{fig:BondPairPlate}
\end{figure}
%
%
\begin{figure}[tbp]
    \centering
    \subinputfrom{\diagrampath/}{bondPairV.eps_tex}
    \caption{Deformation and force vector states}
    \label{fig:Bondpair}
\end{figure}
%
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small.  Because the potential energy and force-states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}.  Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.

\subsection{Energy Equivalence}
%
To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Kirckhoff plate in the \emph{local limit}, i.e. when the nonlocal length scale vanishes.  We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and the plate thickness does not change with deformation.  While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations.  For small vertical displacements we have
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{z(\mathbf{x}+\boldsymbol{\xi})-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi})}{|\boldsymbol{\xi}|},
    \label{eq:beamdtheta}
\end{equation}
%
where $z$ is the vertical displacement of material point.  Taking \(\boldsymbol{\xi}=\xi (\cos(\phi),\sin(\phi))\) in cartesian coordinates and momentarily assuming continuous displacements for the sake of comparison, we use a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta}) about \(\xi = 0\) 
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{\xi}{2} \left(\cos^2(\phi) \kappa_1+\sin^2(\phi) \kappa_2+2\sin(\phi)\cos(\phi)\kappa_3\right)+\mathcal{O}(\xi^3)
    \label{eq:beamdtheta2}
\end{equation}
%
with
%
\begin{equation}
    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
\end{equation}
%
substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
%
\begin{align}
%\label{eq:continuousBeamw}
    w =& \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
    =& \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
    & +4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
\end{align}
%
If we use a weighting function \(\omega(\boldsymbol{\xi})=\omega(\xi)\) and assume that the $\omega$ plays the role of a localization kernel, i.e. $\omega = 0 \; \forall \; \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic plate is
%
\begin{align}
    W =& \alpha \int_{0}^\delta\int_0^{2 \pi} w\; \xi {\rm d}\phi {\rm d}\xi ,\notag \\
    =& \alpha \frac{3\pi}{8} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)\int_{0}^\delta \omega(\xi)\xi^3{\rm d}\xi + \mathcal{O}(\delta^6).\notag 
\end{align}
\todo{It's a little unclear how $m$ arrises below from this equation.  Please see if you can make it more clear.} 
%
Equating $W$ with the classical Kirchoff plate strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
%
\begin{align}
    \lim_{\delta \to 0}  W &= \Omega, \notag \\
    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right), \notag \\
%    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
    \nu = \frac{1}{3},\:\: \alpha &= \frac{16}{3 m} \frac{G h^3}{12(1-\sfrac{1}{3})},
\label{eq:alpha}
\end{align}
%
with 
\begin{equation}
%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
    m = \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag.
\end{equation}

It should be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.

\subsection{Combining Bending and Extension Models}
The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds\todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}, such as in-plane stretch or shear \todo{or you might just say: \dots does not develop membrane forces.}.  If these behaviors are expected in combination with bending, a useful model must resist both.  To create a plate model that also resists these deformations, i.e.\ a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.  In this model, individual bonds act as springs resisting changes in length.
%
\begin{equation}
    \label{eq:bondextension}
    \vstate{T}{}{\boldsymbol{\xi}} =\beta\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|}
\end{equation}
%
By matching the energy of a plate in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the plate.  Following the example of \cite{silling2007peridynamic}, we begin with a plate \todo{should this be shell?} under pure in-plane shear.  In Einstein notation, the strain energy of this plate is
%
%\begin{align*}
%    W^d_\text{C} &= G \; h \; \epsilon_{ij} \epsilon_{ij} = G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
%    W^d_\text{PD} &= \frac{\beta}{2}(\underline{\omega}\; \underline{\epsilon^d})\bullet \underline{\epsilon^d}\\
%    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{\underline{\omega}\langle\xi\rangle}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_\xi\\
%\end{align*}
%
\begin{align*}
    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d,  \\  \\
    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; {\rm d}A_{\boldsymbol{\xi}}, \\
    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;{\rm d}A_{\boldsymbol{\xi}},\\
    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;{\rm d}A_{\boldsymbol{\xi}}.
\end{align*}
%
With $i, j, k, l = 1,2$. For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
%
\begin{align*}
%    m&=(\underline{\omega}\:\underline{x}) \bullet \underline{x}\\
    m &= \int_A \omega(\xi)|\boldsymbol{\xi}|^2\; dA_{\boldsymbol{\xi}} \\
    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11}]\\
    &= \frac{\beta \; m}{16} \epsilon_{ij}^d \epsilon_{kl}^d (\delta_{ij}\delta_{kl}+\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})\\
    &= \frac{\beta \; m}{8} \epsilon_{ij}^d \epsilon_{ij}^d \implies\\
     \beta &= \frac{8 \; G\;h}{m}
\end{align*}
%
Having calibrated the bond-extension model to the shear modulus, applying a different uniform strain (such as might result from uniaxial tension) reveals the bond-based model to result in a one-parameter linearly-elastic model with Poisson's ratio \(\nu=\sfrac{1}{3}\).

Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a plate.  Consider a single bond-pair in the combined model: 
%
\begin{figure}[tbp]
  \label{fig:hybridmodel}
  \centering
  \input{\diagrampath/bondPairCombinedV.tex}
  \caption{The Hybrid Model Combines Bending and Extension Components}
\end{figure}
%
As the two sides are pulled apart, the magnitude of the extension force in each bond increases, and the magnitude of the bending force decreases.  At the same time, the angle at which the extension force acts decreases, and the angle of action for the bending force increases.  For small amounts of bending and reasonable stretches, increased tension in the direction of the bond pair results in increase restorative force.

\section{Extension to arbitrary Poisson ratio}
Although many materials have Poisson ratios of \(\nu\approx \sfrac{1}{3}\), it is nonetheless desirable to extend the model to materials with arbitrary Poisson ratios.  For isotropic, linearly elastic models of solid materials, Silling et al.\ extended the peridynamic material model to arbitrary material parameters in \cite{silling2007peridynamic} by decomposing the deformation into isotropic and deviatoric components.  In the absence of plastic deformation, we need only find the difference between the strain energy of a deformed bond-based plate and the strain energy of an elastic plate with Poisson's ratio \(\nu \neq \sfrac{1}{3}\).  The difference is a function of the isotropic strain in two dimensions, \(\theta_2\)
%
\begin{align}
    W' &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 \notag \\
%    \theta_2 &= \frac{2}{m}\left(\underline{\omega x}\right)\bullet\underline{e} \notag \\
    \theta_2 &= \frac{2}{m}\int_A \omega(\boldsymbol{\xi})|\boldsymbol{\xi}|(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|)\;dA_{\boldsymbol{\xi}} \notag \\
%    W_\text{total} &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 + \frac{4\;G\;h}{m}\left(\underline{\omega e}\right)\bullet\underline{e}\notag
    W_\text{total} &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 + \frac{4\;G\;h}{m}\int_A \omega(\boldsymbol{\xi})(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|)^2\;dA_{\boldsymbol{\xi}}\notag
\end{align}
%
This is to be expected because the bond-based model was calibrated to the shear strain energy, leaving discrepancies proportional to the isotropic strain energy that fall to 0 as Poisson's ratio approaches \(\nu = \sfrac{1}{3}\).
